Using numerical modelling to investigate temperature and wave exposure as drivers

### 2020-01-08 thesis_chapter_1.Rmd
additional housecleaning

---
title: "Quantifying passive kelp rafting phenomena and connectivity of nearshore communities around the coast of South Africa:Development of a 3D spectral numerical coastal-flow model"
author: 
- RM Coppin^[University of the Western Cape]
- C Rautenbach^[South African Weather Service]
- AJ Smit^[University of the Western Cape]
output:
  word_document:
    fig_caption: yes
    reference_docx: chapter_1_template.docx
    toc: yes
  html_document:
    df_print: paged
    toc: yes
    theme:  simplex
bibliography: references.bib
---

>>>>

---
title: Quantifying passive kelp rafting phenomena and connectivity of nearshore communities
  model
  around the coast of South Africa:Development of a 3D spectral numerical coastal-flow
author:
- RM Coppin^[University of the Western Cape]
- C Rautenbach^[South African Weather Service]
- AJ Smit^[University of the Western Cape]
output:
  html_document:
    df_print: paged
    theme: simplex
    toc: yes
  word_document:
    fig_caption: yes
    reference_docx: markdown/thesis_template.docx
    toc: yes
  pdf_document:
    toc: yes
bibliography: references.bib
---

### 2020-01-08 thesis_chapter_2.Rmd
additional housecleaning

---
title: Using numerical modelling to investigate temperature and wave exposure as drivers
  of morphological characteristics of the kelps, Ecklonia maxima and Laminaria pallida
author: "R. Coppin, C. Rautenbach, T. Ponton and A.J Smit"
output:
  word_document:
    reference_docx: markdown/frontiers_template.docx
  html_document:
    df_print: paged
  pdf_document:
    fig_caption: yes
bibliography: references.bib
papersize: A4
tables: yes
abstract:  '**Abstract**: Macroalgal morphological variation is determined to a large extent by
  a combination of environmental factors, with wave exposure and temperature
  perhaps the main influences as they are key environmental properties to which a species becomes locally adapted.                Macroalgae have shown to exhibit different responses to different magnitudes of exposure to waves, such as reduction
  in overall size and strength increasing traits. In terms of temperature, warmer
  environments have been shown to reduce the overall size of resident and transplanted
  species. However, none of the past studies have identified specific wave and temperature
  metrics responsible for the morphological adaptation macroalgae exhibit. Past research
  has often used simple or two-dimensional models of wave exposure, which do not
  take into account important aspects of the nearshore environment such as wave breaking,
  refraction and diffraction. Furthermore, past studies have often used satellite-derived
  datasets as sources for temperature data; however, such data have been shown to have large bias when 
  applied to the nearshore environment. This study used *in situ* temperature data and wave power
  metrics calculated from a 3D-numerical model to identify specific temperature and wave metrics
  responsible for morphological adaptation of the kelp, *Ecklonia maxima* and *Laminaria pallida*. The results identify wave      exposure as the main driver of morphological adaptation while identifying specific wave metrics.
  Furthermore, the results show differences in wave metrics between species; and between
  deep and shallow populations.'

>>>>

---
title: Using numerical modelling to investigate temperature and wave exposure as drivers
  of morphological characteristics of the kelps, Ecklonia maxima and Laminaria pallida
author: "R. Coppin, C. Rautenbach, T. Ponton and A.J Smit"
output:
  html_document:
    df_print: paged
  word_document:
    reference_docx: markdown/frontiers_template.docx
  pdf_document:
    fig_caption: yes
bibliography: references.bib
papersize: A4
tables: yes
abstract:  '**Abstract**: Macroalgal morphological variation is determined to a large extent by
  a combination of environmental factors, with wave exposure and temperature
  perhaps the main influences as they are key environmental properties to which a species becomes locally adapted.                Macroalgae have shown to exhibit different responses to different magnitudes of exposure to waves, such as reduction
  in overall size and strength increasing traits. In terms of temperature, warmer
  environments have been shown to reduce the overall size of resident and transplanted
  species. However, none of the past studies have identified specific wave and temperature
  metrics responsible for the morphological adaptation macroalgae exhibit. Past research
  has often used simple or two-dimensional models of wave exposure, which do not
  take into account important aspects of the nearshore environment such as wave breaking,
  refraction and diffraction. Furthermore, past studies have often used satellite-derived
  datasets as sources for temperature data; however, such data have been shown to have large bias when 
  applied to the nearshore environment. This study used *in situ* temperature data and wave power
  metrics calculated from a 3D-numerical model to identify specific temperature and wave metrics
  responsible for morphological adaptation of the kelp, *Ecklonia maxima* and *Laminaria pallida*. The results identify wave      exposure as the main driver of morphological adaptation while identifying specific wave metrics.
  Furthermore, the results show differences in wave metrics between species; and between
  deep and shallow populations.'
